Corotating Clumps Around Adolescent Low-Mass Stars: Four Years of TESS

### 2023-07-26 paper/ms.tex
update ms

\begin{figure*}[!t]
	\begin{center}
		\centering
		\includegraphics[width=0.9\textwidth]{f8.pdf}
		\vspace{-0.1cm}
		\caption{
			{\bf The magnetic B-star connection}.
			HD~37776 (TIC~11400909) and HD~64740 (TIC~268971806) are
			magnetic B-stars with field geometries dominated by
			high order multipoles.
			Here, we compare their phased TESS light curves against the
			``best-matching'' CQV light curves, selected by eye from
			Figure~\ref{fig:cqvs}.
			Stellar masses approximate to one significant figure are given in the
			lower right of each panel; the star, TESS sector, and period are also noted.
		}
		\label{fig:bstar}
	\end{center}
\end{figure*}

>>>>

\begin{figure}[!t]
	\begin{center}
		\centering
		%\includegraphics[width=0.9\textwidth]{f8.pdf}
		\subfloat{
			\includegraphics[width=0.48\textwidth]{f8a.pdf}
		}

		\vspace{-0.4cm}
		\subfloat{
			\includegraphics[width=0.48\textwidth]{f8b.pdf}
		}
		\vspace{-0.1cm}
		\caption{
      {\bf The magnetic B-star connection}.  HD~37776 and HD~64740 (right column) are
      magnetic B-stars with field geometries dominated by high order
      multipoles.
			Here, we compare their phased TESS light curves against the
			``best-matching'' CQV light curves (left column), selected by eye from
			Figure~\ref{fig:cqvs}.
      Stellar masses rounded to one significant figure are given
      in the lower right of each panel; the star, TESS sector, and
      period are listed in the title.
		}
		\label{fig:bstar}
	\end{center}
\end{figure}
